Avoiding tipping points in fisheries management through Gaussian Process Dynamic Programming

### 2014-11-14 manuscripts/manuscript.Rmd
include pdf

```{r figure_3, dependson = c("assemble-opt"), fig.cap="The steady-state optimal policy (infinite boundary) calculated under each model.  Policies are shown in terms of target escapement, $S(t)$, as under models such as this a constant escapement policy is expected to be optimal [@Reed1979] Several policies show a numerical jitter due to the discritization of states in the dynamic programming algorithm; doubling the number of grid points did not qualitatively change the results.", fig.width=8, fig.height=6, cache=FALSE}
policies <- melt(data.frame(stock=x_grid, sapply(OPT, function(x) x_grid[x])), id="stock")
names(policies) <- c("stock", "method", "value")

>>>>

```{r figure_3, dependson = c("assemble-opt"), fig.cap="The steady-state optimal policy (infinite boundary) calculated under each model.  Policies are shown in terms of target escapement, $S(t)$, as under models such as this a constant escapement policy is expected to be optimal [@Reed1979] Several policies show a numerical jitter due to the discretization of states in the dynamic programming algorithm; doubling the number of grid points did not qualitatively change the results.", fig.width=8, fig.height=6, cache=FALSE}
policies <- melt(data.frame(stock=x_grid, sapply(OPT, function(x) x_grid[x])), id="stock")
names(policies) <- c("stock", "method", "value")

### 2014-11-14 manuscripts/manuscript.tex
include pdf

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_3-1.pdf}
\caption{The steady-state optimal policy (infinite boundary) calculated
under each model. Policies are shown in terms of target escapement,
$S(t)$, as under models such as this a constant escapement policy is
expected to be optimal (Reed 1979).}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_3-1.pdf}
\caption{The steady-state optimal policy (infinite boundary) calculated
under each model. Policies are shown in terms of target escapement,
$S(t)$, as under models such as this a constant escapement policy is
expected to be optimal (Reed 1979) Several policies show a numerical
jitter due to the discretization of states in the dynamic programming
algorithm; doubling the number of grid points did not qualitatively
change the results.}
\end{figure}
